---
title: "Model_Recov"
author: "Simon"
date: "26/10/2021"
output: 
  html_document:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(message = FALSE)

pacman::p_load("tidyverse","viridis","sjPlot","BayesFactor")

```

## Models

This file checks if models could recover. We simulated choices for all subjects from the fitted data.
Directories may change becaue i try to make everything consistent without breaking stuff. 

```{r adolescents}
#kernelnames<-c("GP", "BMT")
#names of all acquisition functions
#acqnames<-c("GM", "EG", 'UCB')
RBF_UCB<-NULL
BMT_UCB<-NULL
RBF_GM<-NULL
RBF_EG<-NULL
newModels=c("BMT-UCB","RBF-UCB","RBF-GM","RBF-EG")
newModelList=list()

#newModelList[[1]]=list(rbf,ucb,"RBF","UCB")
#newModelList[[2]]=list(rbf,greedyMean,"RBF","GM")
#newModelList[[3]]=list(rbf,epsilonGreedy,"RBF","EG")
#newModelList[[4]]=list(bayesianMeanTracker,ucb,"BMT","UCB")
####
#### This was a bug! I mixed up the models when saving the files.
#### 
actualModels=c("RBF-UCB","RBF-GM","RBF-EG","BMT-UCB")

WhichPrefix<-c("","Meder","Schulz")
#for (i in 1:3){
i=1
for (prefix in WhichPrefix){
  #that is because i made an error
  if(prefix=="Meder"){
    suffix="_data" # another bug. accidentally saved the wrong datafiles i have been all over the place
  }else{
    suffix=""
  }
  
  RBF_UCB<-rbind(RBF_UCB,list.files(path = "./modelRecovery/modelRecovery/", pattern = paste0("*BMT-UCB_",i,suffix,".rds"))%>%
                   Filter(function(x){str_detect(x,paste0("^",prefix))},.)%>%#check which experiment
                   purrr::map(~ readRDS(paste0("./modelRecovery/modelRecovery/",.x)))%>%
                   do.call("rbind",.)%>%
                   mutate(simModel="RBF-UCB",
                          id=as.numeric(paste0(uid,i)),
                          exp=prefix))
  
  RBF_GM<-rbind(RBF_GM,list.files(path = "./modelRecovery/modelRecovery/", pattern = paste0("*RBF-UCB_",i,suffix,".rds"))%>%
                  Filter(function(x){str_detect(x,paste0("^",prefix))},.)%>%#check which experiment
                  purrr::map(~ readRDS(paste0("./modelRecovery/modelRecovery/",.x)))%>%
                  do.call("rbind",.)%>%
                  mutate(simModel="RBF-GM",id=as.numeric(paste0(uid,i)),exp=prefix))
  
  RBF_EG<-rbind(RBF_EG,list.files(path = "./modelRecovery/modelRecovery/",pattern = paste0("*RBF-GM_",i,suffix,".rds"))%>%
                  Filter(function(x){str_detect(x,paste0("^",prefix))},.)%>%#check which experiment
                  purrr::map(~ readRDS(paste0("./modelRecovery/modelRecovery/",.x)))%>%
                  do.call("rbind",.)%>%mutate(simModel="RBF-EG",id=as.numeric(paste0(uid,i)),exp=prefix
                  ))
  
  BMT_UCB<-rbind(BMT_UCB,list.files(path = "./modelRecovery/modelRecovery/",pattern = paste0("*RBF-EG_",i,suffix,".rds"))%>%
                   Filter(function(x){str_detect(x,paste0("^",prefix))},.)%>%#check which experiment
                   purrr::map(~ readRDS(paste0("./modelRecovery/modelRecovery/",.x)))%>%
                   do.call("rbind",.)%>%mutate(simModel="BMT-UCB",id=as.numeric(paste0(uid,i)),exp=prefix))
  
}
#}

#list.files(path = "./modelRecovery/modelRecovery/", pattern = paste0("*BMT-UCB_",i,".rds"))

#list.files(path = "./modelRecovery/",pattern = "*Kernel1_Aqui_3_1.rds")
```

#compute which model was best

```{r}
RecoveryDF<-rbind(RBF_UCB,BMT_UCB,RBF_GM,RBF_EG)%>%
  #filter(exp!="Meder")%>%
  rowwise()%>%
  dplyr::mutate(fitModel=paste0(kernel,"-",aq))%>%
  #filter(fitModel=="RBF_UCB"|fitModel=="BMT_UCB")%>%
  dplyr::group_by(uid,fitModel,simModel,V1)%>%
  dplyr::mutate(n=n())%>%
  select(-c(value,name))%>%
  unique()%>%
  dplyr::group_by(uid,fitModel,simModel)%>%
  #SC: we dont compoute the BIC mutate(BIC=log(25*10)*n+2*V2)%>%#25*8= one trial had 25 choices, 8 for each CV round we
  dplyr::summarise(m=sum(V2))%>%
  #arrange(simModel,uid)%>%#filter(simModel=="RBF_UCB")%>%
  dplyr::group_by(uid,simModel)%>%
  dplyr::mutate(modelBest=ifelse(m==min(m),1,0))%>%
  dplyr::group_by(fitModel,simModel)%>%
  dplyr::summarise(meanB=mean(modelBest))%>%ungroup()

#RecoveryDF%
```

## plot

```{r}
RecoveryDF%>%
  ggplot(aes(x=simModel,y=fitModel,fill=meanB))+
  geom_tile()+
  geom_text(aes(label = round(meanB, 2)))+
  scale_fill_viridis(name="p(fit|gen)")+
  theme_blank(14)+
  scale_x_discrete(name="generative model",breaks=c("RBF-UCB","RBF-GM","BMT-UCB","RBF-EG"),labels = expression('GP-UCB', lambda*' lesion', beta* ' lesion', tau*' lesion'))+
  scale_y_discrete(name="fitted model",breaks=c("RBF-UCB","RBF-GM","BMT-UCB","RBF-EG"),labels = expression('GP-UCB', lambda*' lesion', beta* ' lesion', tau*' lesion'))+
  theme(aspect.ratio = 1)->confMAll
```


```{r}
InversionMatrix<-NULL
# compute probability that a model fits best given it generated the data
for (i in unique(RecoveryDF$fitModel)){
  subset=RecoveryDF[RecoveryDF$fitModel==i,]
  subset$inversionProb=99
  for (j in unique(RecoveryDF$simModel)){
    #devide model of interests best fit by the columnsum. (Bayes theorem)
    subset[subset$simModel==j,]$inversionProb=(subset[subset$simModel==j,]$meanB)/sum(subset$meanB)
  }
  InversionMatrix=rbind(InversionMatrix,subset)
}

InversionMatrix%>%rowwise()%>%mutate(inversionProb=case_when(is.na(inversionProb)~0,
                                                             TRUE~inversionProb)
)%>%
  ggplot(aes(x=simModel,y=fitModel,fill=inversionProb))+
  geom_tile()+
  geom_text(aes(label = round(inversionProb, 2)))+
  scale_fill_viridis(name="p(gen|fit)",option="plasma")+
  scale_x_discrete(name="generative model",breaks=c("RBF-UCB","RBF-GM","BMT-UCB","RBF-EG"),labels = expression('GP-UCB', lambda*' lesion', beta* ' lesion', tau*' lesion'))+
  scale_y_discrete(name="fitted model",breaks=c("RBF-UCB","RBF-GM","BMT-UCB","RBF-EG"),labels = expression('GP-UCB', lambda*' lesion', beta* ' lesion', tau*' lesion'))+
  theme_blank(14)+
  theme(aspect.ratio = 1)->invMAll
```

# All experiments
```{r fig.width=10, fig.height=5}
matrix<-cowplot::plot_grid(confMAll,invMAll,labels=c("a","b"))
matrix

ggsave(matrix,filename = "X_Figures/Confusion_InversionAll.pdf",width = 10,height = 5)
```

# Model recovery only GP & BMT but by experiment.

#compute which model was best

```{r}
conf_ByExp<-list()
inv_ByExp<-list()

experiments=c("Adolescent Data","Meder et al. (2021)","Schulz et al. (2019)")
for (cnt in 1:length(experiments)){
  RecoveryDF<-rbind(RBF_UCB,BMT_UCB,RBF_GM,RBF_EG)%>%mutate(exp=case_when(exp==""~experiments[1],
                                                                          exp=="Meder"~experiments[2],
                                                                          exp=="Schulz"~experiments[3]))%>%
    filter(exp==experiments[cnt])%>%
    rowwise()%>%
    dplyr::mutate(fitModel=paste0(kernel,"-",aq))%>%
    #filter(fitModel=="RBF_UCB"|fitModel=="BMT_UCB")%>%
    dplyr::group_by(uid,fitModel,simModel,V1)%>%
    dplyr::mutate(n=n())%>%
    select(-c(value,name))%>%
    unique()%>%
    dplyr::group_by(uid,fitModel,simModel)%>%
    #SC: we dont compoute the BIC mutate(BIC=log(25*10)*n+2*V2)%>%#25*8= one trial had 25 choices, 8 for each CV round we
    dplyr::summarise(m=sum(V2))%>%
    #arrange(simModel,uid)%>%#filter(simModel=="RBF_UCB")%>%
    dplyr::group_by(uid,simModel)%>%
    dplyr::mutate(modelBest=ifelse(m==min(m),1,0))%>%
    dplyr::group_by(fitModel,simModel)%>%
    dplyr::summarise(meanB=mean(modelBest))%>%ungroup()
  
  RecoveryDF%>%
    ggplot(aes(x=simModel,y=fitModel,fill=meanB))+
    geom_tile()+
    geom_text(aes(label = round(meanB, 2)))+
    scale_fill_viridis(name="p(fit|gen)",limits=c(0,1))+
    scale_x_discrete(name="generative model",breaks=c("RBF-UCB","RBF-GM","BMT-UCB","RBF-EG"),labels = expression('GP-UCB', lambda*' lesion', beta* ' lesion', tau*' lesion'))+
    scale_y_discrete(name="fitted model",breaks=c("RBF-UCB","RBF-GM","BMT-UCB","RBF-EG"),labels = expression('GP-UCB', lambda*' lesion', beta* ' lesion', tau*' lesion'))+  
    theme_blank(14)+
    theme(aspect.ratio = 1)->confM
  
  InversionMatrix<-NULL
  # compute probability that a model fits best given it generated the data
  for (i in unique(RecoveryDF$fitModel)){
    subset=RecoveryDF[RecoveryDF$fitModel==i,]
    subset$inversionProb=99
    for (j in unique(RecoveryDF$simModel)){
      #devide model of interests best fit by the columnsum. (Bayes theorem)
      subset[subset$simModel==j,]$inversionProb=(subset[subset$simModel==j,]$meanB)/sum(subset$meanB)
    }
    InversionMatrix=rbind(InversionMatrix,subset)
  }
  
  InversionMatrix%>%rowwise()%>%mutate(inversionProb=case_when(is.na(inversionProb)~0,
                                                               TRUE~inversionProb)
  )%>%
    ggplot(aes(x=simModel,y=fitModel,fill=inversionProb))+
    geom_tile()+
    geom_text(aes(label = round(inversionProb, 2)))+
    scale_fill_viridis(name="p(gen|fit)",option="plasma",limits=c(0,1))+
    theme_blank(14)+
    scale_x_discrete(name="generative model",breaks=c("RBF-UCB","RBF-GM","BMT-UCB","RBF-EG"),labels = expression('GP-UCB', lambda*' lesion', beta* ' lesion', tau*' lesion'))+
    scale_y_discrete(name="fitted model",breaks=c("RBF-UCB","RBF-GM","BMT-UCB","RBF-EG"),labels = expression('GP-UCB', lambda*' lesion', beta* ' lesion', tau*' lesion'))+
    theme(aspect.ratio = 1)->invM
  
  #print(i)
  conf_ByExp[[cnt]]<-confM
  inv_ByExp[[cnt]]<-invM
}

confLeg<-get_legend(conf_ByExp[[1]]+theme_classic(10)+theme(legend.position = c(0.5,0.6)))
invLeg<-get_legend(inv_ByExp[[1]]+theme_classic(10)+theme(legend.position = c(0.5,0.6)))

```

# join figure

```{r}
library(gridExtra)
library(grid)
#make plowtwise y axis labels

row1<-cowplot::plot_grid(confMAll+theme(legend.position="none",axis.title.x = element_text(color="white")),invMAll+theme(legend.position="none"),nrow=2,rel_heights = c(1,1),labels=c("",""))
row1tit<-grid.arrange(arrangeGrob(row1, top = textGrob(label='All dataasets',hjust = 0.2,gp = gpar(col = "black", fontsize = 16))))

row2<-cowplot::plot_grid(conf_ByExp[[1]]+theme(legend.position="none",axis.title.y = element_text(color="white"),axis.title.x = element_text(color="white")),inv_ByExp[[1]]+theme(legend.position="none",axis.title.y = element_text(color="white")),nrow=2,rel_heights = c(1,1),labels=c("",""))
row2tit<-grid.arrange(arrangeGrob(row2, top = textGrob(label='Adolescent data',hjust = 0.2,gp = gpar(col = "black", fontsize = 16))))

row3<-cowplot::plot_grid(conf_ByExp[[2]]+theme(legend.position="none",axis.title.y = element_text(color="white"),axis.title.x = element_text(color="white")),inv_ByExp[[2]]+theme(legend.position="none",axis.title.y = element_text(color="white")),nrow=2,rel_heights = c(1,1),labels=c("",""))
row3tit<-grid.arrange(arrangeGrob(row3, top = textGrob(label='Meder et al (2021)',hjust = 0.2,gp = gpar(col = "black", fontsize = 16))))

row4<-cowplot::plot_grid(conf_ByExp[[3]]+theme(legend.position="none",axis.title.y = element_text(color="white"),axis.title.x = element_text(color="white")),inv_ByExp[[3]]+theme(legend.position="none",axis.title.y = element_text(color="white")),nrow=2,rel_widths = c(1,0.3),labels=c("",""))
row4tit<-grid.arrange(arrangeGrob(row4, top=textGrob(label='Schulz et al (2019)',hjust = 0.2,gp = gpar(col = "black", fontsize = 16))))

rowleg<-cowplot::plot_grid(confLeg,invLeg,nrow=2)

```

```{r fig.height=4,fig.width=8.5}
cowplot::plot_grid(row1,row2,row3,row4,rowleg, nrow=1,rel_widths = c(1,1,1,1,0.3))

ggsave(filename="X_Figures/Experiments_Seperate.pdf",height=8,width=17)
#ggsave(filename="X_Figures/Experiments_Seperate.png",height=8,width=15)

```

```{r}
InversionMatrix<-NULL
# compute probability that a model fits best given it generated the data
for (i in unique(RecoveryDF$fitModel)){
  subset=RecoveryDF[RecoveryDF$fitModel==i,]
  subset$inversionProb=99
  for (j in unique(RecoveryDF$simModel)){
    #devide model of interests best fit by the columnsum. (Bayes theorem)
    subset[subset$simModel==j,]$inversionProb=(subset[subset$simModel==j,]$meanB)/sum(subset$meanB)
  }
  InversionMatrix=rbind(InversionMatrix,subset)
}

InversionMatrix%>%rowwise()%>%mutate(inversionProb=case_when(is.na(inversionProb)~0,
                                                             TRUE~inversionProb)
)%>%
  ggplot(aes(x=simModel,y=fitModel,fill=inversionProb))+
  geom_tile()+
  geom_text(aes(label = round(inversionProb, 2)))+
  scale_fill_viridis(name="p(gen|fit)",option="plasma")+
  theme_blank()+
  theme(axis.text.x = element_text(angle = 45,hjust = 1),aspect.ratio = 1)->invM

### collect the plots in a list
RecoveryDF%>%
  ggplot(aes(x=simModel,y=fitModel,fill=meanB))+
  geom_tile()+
  geom_text(aes(label = round(meanB, 2)))+
  scale_fill_viridis(name="p(fit|gen)")+
  theme_blank()+
  theme(axis.text.x = element_text(angle = 45,hjust = 1),aspect.ratio = 1)->confM
```


# Bayes factor modelcomparison
That does not look super convincing but its already a start.
Lets do it how eric did it. Quick reminder: he t-tested every model against each other and did not group by the generative model.
Could actually also be something to show. How many figures can we have?

```{r}
modelspace=c("GP-UCB","BMT-UCB","GP-GM","BMT-GM","GP-GV","BMT-GV")
#modelspaceFi=c("RBF_UCB","BMT_UCB","RBF_GM","BMT_GM","RBF_GV","BMT_GV")
t_test=list()
for (fittedModel in 1:length(modelspace)){
  for (simulatedModel in 1:length(modelspace)){
    t_test[[fittedModel]]<-
      rbind(RBF_UCB,BMT_UCB,RBF_GM,BMT_GM,RBF_GV,BMT_GV)%>%rowwise()%>%
      mutate(fitModel=paste0(kernelnames[kernel],"_",acqnames[aq]))%>%
      group_by(simModel,fitModel,id)%>%summarize(mFit=mean(V2))%>%
      filter(simModel==modelspace[simulatedModel] & (fitModel==modelspace[fittedModel] | fitModel==modelspace[simulatedModel]))#%>%
    #pivot_wider(names_from = "fitModel",values_from="mFit")
  }
}



BF_modelComp<-tibble()

for (fittedModel in 1:length(modelspace)){
  for (simulatedModel in 1:length(modelspace)){
    testDf<-rbind(RBF_UCB,BMT_UCB,RBF_GM,BMT_GM,RBF_GV,BMT_GV)%>%rowwise()%>%
      mutate(fitModel=paste0(kernelnames[kernel],"-",acqnames[aq]))%>%
      group_by(simModel,fitModel,id)%>%
      summarize(mFit=mean(V2))%>%
      filter(simModel==modelspace[simulatedModel] & 
               (fitModel==modelspace[fittedModel] | fitModel==modelspace[simulatedModel]))%>%
      pivot_wider(names_from = "fitModel",values_from="mFit")%>%
      ungroup()
    #compute bayesfactor
    if(ncol(testDf)==4){
      huh<-BayesFactor::ttestBF(x=pull(testDf%>%select(modelspace[fittedModel])),y=pull(testDf%>%select(modelspace[simulatedModel])),paired = T)
      #concat.
      BF_modelComp<-rbind(BF_modelComp,tibble(bf=huh@bayesFactor[["bf"]],
                                              simMod=modelspace[simulatedModel],fitmod=modelspace[fittedModel]))
    }else{
      BF_modelComp<-rbind(BF_modelComp,tibble(bf=NaN,simMod=modelspace[simulatedModel],fitmod=modelspace[fittedModel]))
    }
  }
}
```

# model recovery bayes factor
```{r}
BF_modelComp%>%
  ggplot(aes(x=simMod,y=fitmod,fill=bf))+
  geom_tile()+
  geom_text(aes(label = round(bf, 2))) +
  scale_fill_gradient2()

```
